\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{ragged2e}
\renewcommand{\familydefault}{\sfdefault}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{-0.4em}\rule{\linewidth}{0.4pt}\vspace{0.3em}]
\titlespacing*{\section}{0pt}{1ex}{0.5ex}
\setlength{\parskip}{0.3ex}
\begin{document}
\RaggedRight

% Name + Title
\begin{center}
  {\LARGE\bfseries NGO DUC DUNG}\\[4pt]
  {\normalsize Software Engineer}
\end{center}
\vspace{4pt}

% Contact
\begin{center}
  {\small
    \texttt{+84 377 369 365} \quad | \quad \texttt{dungngo4520@gmail.com} \quad | \quad Hanoi, VN\\[3pt]
    \href{https://github.com/dungngo4520}{github.com/dungngo4520} \quad | \quad \href{https://linkedin.com/in/dungngo4520}{linkedin.com/in/dungngo4520}\\[3pt]
  }
\end{center}
\vspace{6pt}

\section*{Profile}
\noindent
Systems engineer with 4+ years building system-level software for Linux and Windows kernels. Built kernel drivers, real-time malware scanners, and telemetry services; focus on speed and reliability. Shipped work to thousands of endpoints and cut customer-impacting crashes to 0\%.

\section*{Core Skills}
\noindent
% Core skills grouped for scannability (expanded with senior-level items)
\textbf{Languages:} C, C++, Go, Rust, Python, Shell, SQL, Zig\\
\textbf{Platforms / Frameworks:} Windows kernel (WDM, WDF, WFP, FS Filter), Linux kernel modules, user-space daemons, Qt\\
\textbf{Debugging / Profiling:} Low-level debugging (WinDbg, WPA/WPR, perf, eBPF, ETW), x64dbg, gdb, IDA\\
\textbf{Tools / DevOps:} Git, Jira, Jenkins, Docker, CI/CD, unit \& integration tests, observability\\
\textbf{Architecture / Design:} Systems architecture design; distributed log/telemetry pipeline design; multithreaded systems; microservices; Strategy/Pipeline/State patterns\\
\textbf{Security / Practices:} Secure development (sandboxing, privilege boundaries); malware analysis; memory \& file scanning
\section*{Professional Experience}
\noindent
\textbf{Viettel Cyber Security} \hfill \textit{Software Engineer} \\
\textit{Endpoint Security Services (EDR, EPP, EDP)} \hfill 2021 -- Present \\
\textit{Project:} Endpoint Security Services - collects endpoint logs and activities, detects and protects against malware, and provides operators with telemetry and response tools. \textit{Team size:} 20.

\begin{itemize}[leftmargin=*,noitemsep]
  \item Responsibilities: Device Control, Endpoint Firewall, Web Protection, Anti-Ransomware (kernel-level protection features).
  \item Mentored new team members, ran code reviews, and helped set coding standards and onboarding practices to improve code quality and ramp-up time.
  \item Built Windows kernel drivers for protection features and deployed to thousands of endpoints; maintained a 0\% customer-impacting crash rate.
  \item Rewrote the Linux log-collection subsystem as a stable kernel module - eliminated production hangs and improved telemetry reliability.
  \item Implemented a multithreaded real-time malware scanner on Linux - made scans ~20\% faster and reduced latency so scanning works in real time.
  \item Tuned log processing and telemetry pipelines to lower CPU and memory use and improve stability under heavy load.
  \item Built CI/CD pipelines with Jenkins and Docker and added automated tests to reduce regressions and speed releases. Follow agile/Scrum processes.
\end{itemize}

\section*{Education}
\noindent
\textbf{University of Engineering and Technology, Vietnam National University} \hfill 2018 -- 2022\\
Bachelor of Information Technology, graduated with distinction; GPA: 3.21

\section*{Other}
\noindent
\textbf{Languages:} Vietnamese (native), English (professional)

\end{document}
